%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                            %%
%%                                Sample Essay                                %%
%%                                                                            %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PACKAGES AND GLOBALS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{essay}
\usepackage[margin=1in]{geometry}
\IfFileExists{config.tex}{\input{config.tex}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% START
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\sffamily


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% HEADER
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbigheader{Sample Essay}{from \textit{The Hundred Headless Woman}}{Max Ernst}
% \setsmallheader{Sample Essay}{from \textit{The Hundred Headless Woman}}{Max Ernst}

\setbodyheader{Max Ernst}{from \textit{The Hundred Headless Woman}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% BODY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{essaystyle}

Crime or miracle: a complete man. The immaculate conception that failed, failed
and failed again. Then the landscape changes three times, one, two and three,
and the sky takes its hat off twice, one and two. Therefore the semi-fecund
lamb dilating at will his abdomen becomes a ewe and Loplop, the best bird,
brings the mighty repast to the streetlamps in the basin of Paris. At the same
time: the immaculate conception.

Extreme unction for extreme youth. The great St.\@ Nicolas, followed by
impeccable parasites, is led by his two lateral appendices. Remember: to
disemboweled baby dove-cote is open, and when one sees a charming little insect
with metallic hair, then the unconsciousness of the landscape becomes complete.
Here in preparation the first touches of grace and games without issue. Bring
the wash to a boil and increase the charm of transportation and the silence of
bleeding wounds, and go on and on with the daytime games, twilight and
nocturnal. Odor of dried flowers --- or I want to be Queen of Sheba. Germinal,
my sister, the 100-headless woman. In a cage in the background: God the father.
New series of daytime games, twilight and nocturnal. Continuation!
Continuation! During the day angelic caresses retire to secret regions near the
poles. Continuation! Fiesta coiled in bracelets around branches --- Prometheus
--- the 100-headless woman opens her august sleeves. (This monkey, could he by
chance be Catholic?) The exorbitant recompense: Perturbation, my sister, the
100-headless woman.

Without a word and in any weather: magic light. Without a word and in any
weather: obscure lessons. Sunday phantoms shriek. Dear granny! In cadence more
than one passing notary lets his voice drop. Suddenly Loplop reappears with the
mouse's horoscope. When the third mouse sits, the body of a legendary grown-up
woman flies by. Then let me introduce you to my uncle whose beard we love to
tickle on Sunday afternoons. We had hardly strangled the uncle when the
marvelous young women flew away. Call it witchcraft or some macabre joke, when
suddenly a wide cry of the great diameter stifles the fruits and meat in their
coffins. We'll begin then with a little family-party, with physical culture or
the death that you prefer. Have a rapid look at the hibernians of this island
and catch the numb train (registration of baggage is worth title of nobility).
Open your bag, my brave man, catch the yacht and see the rising sap. Loplop the
swallow passes. Nourishing themselves on liquid dreams and quite resembling
sleeping leaves, here are my seven sisters together. Loplop the swallow
returns.

Loplop the best bird chases in terror the last vestiges of the communal
devotion, the sphinx and the daily bread visit the convent and God the father,
his beard furrowed with lightning, continues in a subway catastrophe.

Loplop meets the belle jardiniere.

Almost alone with the phantoms and ants: Germinal, my sister, the 100-headless
woman. The moon is beautiful. And the volcanic women with a menacing air raise
and agitate the backpart of their bodies.

Nothing can stop the passing smile which accompanies the crimes from one sex to
the other, the unlimited meetings and robust effervescences in the supposedly
poisoned wheel, and public discharges at any place (all places equal). And
Loplop, the best bird, made himself fleshless flesh to live amongst us. His
smile will be elegantly sober. His arm will be drunkness, his sting fire. His
look will descend straight into the debris of the parched cities.

Living alone on her phantom-globe, beautiful garbed in her dreams,
Perturbation, my sister, the 100-headless woman. Every bloody revolt will make
her live endowed with grace and truth. Her smile, the fire, will fall like
black jelly and white rust on the flanks of the mountain, and her phantom-globe
will find us at every halting place.

Lighter than air, powerful and isolated: Perturbation, my sister, the
100-headless woman.  But the waves are bitter, the truth will remain simple and
gigantic wheels will furrow the bitter waves. And the images will descend even
to the ground. Every Friday the titans will travel over our laundries in a
rapid flight with many hooks. And nothing will be more common than a titan in a
restaurant. In the blindness of the wheelwrights we will find the germs of very
precious visions. The blacksmiths, grey, black or volcanic, will turn in the
air over the forges and forge crowns even larger as they rise higher.

More powerful than vulcans, light and isolated, Perturbation, my sister, the
100-headless woman. Perturbation, elevation, diminishment. Rumbling of drums in
the stones, dilapidations, Aurora and a phantom excessively meticulous.
Tranquility of ancient and future assassinations. Pieces of conviction. The
departure for the miraculous fishing-voyage.  More isolated than the sea,
always light and strong, Perturbation, my sister, the 100-headless woman.

Here is thirst, that resembles me, the miraculous fishing, clamors and love,
the jubilant and gracious thunder, the master of the night, the sea of
serenity, the elegant gesture of the drowned, serenity, the sea of jubilation.

The night howls in its hiding-place and approaches our eyes like wounded flesh.
A door opens itself backwards by the night of silence. A bodiless body places
himself parallel to his body and shows us --- like a phantomless phantom with
particular saliva --- the matrix for postage stamps. Two bodiless bodies place
themselves parallel to their bodies, falling out of beds and curtains --- like
phantomless phantoms.

The 100-headless woman would smile in her sleep so that Loplop might smile at
the phantoms.

Loplop, drunk with fright and fury, recovers his birdshead and remains immobile
for 12 days at both sides of the door. Then the forest opens itself before an
accomplished couple followed by a blind body.

To evoke the seventh age which succeeds the ninth birth, Germinal of the
invisible eyes, the moon and Loplop trace ovals with their heads. At this
moment the phantoms enter a period of voracity. Sometimes naked, sometimes clad
in thin jets of fire, they make the geysers spout with the probability of
bloodrain and with the vanity of the dead. To the glamour of their scales they
prefer the dust of carpets, to the masturbation of fresh leaves, the pious
lies. But they escape with fear as soon as the rumbling of drums is heard under
the water. They pick up some dry crackers in the hollows of the giant's
causeway. The giant's causeway is a pile of cradles.

Therefore the phantom remains who speculates with the vanity of death, the
phantom of repopulation. All the doors are doors and the butterflies start to
sing. After a slight hesitation, you will identify among these phantoms:
Pasteur in his workroom, the monkey who is a future policeman, Catholic or
stockbroker, Phantomas, Dante and Jules Verne, Cezanne and Rosa Bonheur, Mata
Hari, St.\@ Lazarus gloriously resuscitated from the dromedary's droppings.

Let it hereby be known, that since the memory of mankind the 100-headless woman
has never had relations with the phantom of repopulation. She will never have.
Rather would she macerate herself in morning dew and nourish herself with iced
violets.

Let us thank Satanas and be happy for the sympathy he has shown us (bis).

Eyeless eye, the 100-headless woman keeps her secret (ter).

Eyeless eye, the 100-headless woman and Loplop go back to the savage stage and
cover the eyes of their faithful birds with fresh leaves. God the almighty
tries in vain to separate light from darkness.

Eyeless eye, the 100-headless woman keeps her secret.

She keeps her secret.

She keeps it.

Rome --- Rome --- Paris --- marsh of dreams.

Ask the monkey: who is the 100-headless woman? In the church-fathers' manner he
will answer you: It suffices me to look at her and I know who she is. It
suffices for you to demand of me an explanation, and I no longer know.

Loplop the sympathetic annihilator and ancient best bird shoots some elderballs
into some debris of the universe.

\end{essaystyle}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% END
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}
